\documentclass[11pt,a4paper]{article}
\usepackage{geometry}
\usepackage{url}

\title{UPDATES from 2013/2014 School Year}
\author{Organizers: Vincenzo Coia, Andy Leung}
\date{\today}

\begin{document}

\maketitle

\section{Overview}

The first cycle of GWF was started on April 17, 2014 and has now completed on July 22, 2014. In this cycle, we have 10 students participated in the brainstorming session to select potential forum branches. Three potential branches were proposed:
\begin{itemize}
\item Curriculum Vitae,
\item Grant application writing, and
\item Notation and mathematical convention. 
\end{itemize}
An on-line survey was set up to select the branch with the most responses and seven students (a different set of students) responded. Both Grant application writing and Notation and mathematical convention had four votes, but the facilitators decided to choose the former one to proceed on. The four votes were Neil Spencer, Camila Casquilho, Seong Hwan-Jun, and one anonymous student. Neil Spencer kindly volunteered to be the branch leader. The group then chose Professor John Petkau to be the speaker for the workshop. John kindly accepted the invitation and gave the workshop on June 19, 2014. Two students from the group (Neil Spencer and Camila Casquilho) and the three facilitators (Estella Qi, Vincenzo Coia, and Andy Leung) participated in the workshop. Overall, the workshop was successful -- John answered all the questions that the group had prepared. Following the workshop, only two students (Seong and Andy) were interested in the feedback session where the students give and receive feedback on a small piece of work he/she has made changes to. The feedback session was held on July 22, 2014. 

\section{Some tips}

The response rate of the feedback session was low. The organizers could consider having the feedback session on the same day of the workshop. 





\end{document}
